### 2014-04-01 ApTranscriptome_TR.Rmd
Continuing work. Moved `RxNtype` function (used in `ldply`) to scripts.
Error message about "split_labels" to debug

```{r lmFunc}
# first, define function to use
lmFunc <- function(bar) {
  # fit lm
  lmout <- eval(parse(text = paste("lm(", model, ", data = bar)", sep = "")))

  # stepAIC to drop non-significant terms
  f.lmout <- stepAIC(lmout)

  # return final model
  return(f.lmout) 
}

@@

test.transcripts <- temperature.transcripts[1:10]

response.type <- ldply(test.transcripts, .progress = "text", RxNtype)

RxNtype <- function(lmitem) {
  # predict 
  pred.vals <- seq(from = 0, to = 38.5, by = 0.5)
  newdf <- data.frame(val = pred.vals, colony = as.factor(rep(unlist(lmitem$xlevels), each = length(pred.vals))))
  pout <- predict(lmout, newdata=newdf)
  pout <- cbind(newdf, pTPM = pout)

  max.val
  # for each colony
  for(c in levels(pout$colony)) {

    # get max val
    max.val <- pout[which(pout$pTPM == max(pout$pTPM)), "val"]
    # get min val
    min.val <- pout[which(pout$pTPM == min(pout$pTPM)), "val"]
    # determine expression shape
    exp_type <- NA
    # expression type defined as "Bimodal" if max expression below 10C and above 30C is greater than 2 standard deviations above expression at the optimum temperature (19.5C)
    if(max(pout[pout$val < 10, "pTPM"]) > (pout[pout$val == 19.5, "pTPM"] + 2*sd(pout$pTPM)) & max(pout[pout$val > 10, "pTPM"]) > (pout[pout$val == 19.5, "pTPM"] + 2*sd(pout$pTPM)))   exp_type <- "Bimodal" else {
      # expression type "High" if max expression at temperature above 30C
      if(max.val > 30) exp_type <- "High" else {
        # expression type "Low" if max expression at temperature below 10C
        if(max.val < 10) exp_type <- "Low" else
          exp_type <- "Intermediate"
        } # end else
      } # end else
    }
  }

# plot
#qplot(val, pTPM, facets = .~colony, data = pout, geom="smooth")

@@

# apply the 'RxNply' function to determine maximum and minimum temperatures of expression, as well as the expression level at the optimum temperature of 19.25C
temperature.transcripts.type <- ddply(temperature.transcripts.TPM, .(Transcript), RxNply)
temperature.transcripts.type$max.val <- as.numeric(temperature.transcripts.type$max.val)
temperature.transcripts.type$min.val <- as.numeric(temperature.transcripts.type$min.val)
temperature.transcripts.type$opt.exp <- as.numeric(temperature.transcripts.type$opt.exp)
temperature.transcripts.type$exp_type <- as.factor(temperature.transcripts.type$exp_type)

# repeat for transcripts that have an interaction with colongy
# A22
A22.interaction.transcripts.type <- ddply(interaction.transcripts.TPM["A22"], .(Transcript), RxNply)
A22.interaction.transcripts.type$max.val <- as.numeric(A22.interaction.transcripts.type$max.val)
A22.interaction.transcripts.type$min.val <- as.numeric(A22.interaction.transcripts.type$min.val)
A22.interaction.transcripts.type$opt.exp <- as.numeric(A22.interaction.transcripts.type$opt.exp)
A22.interaction.transcripts.type$exp_type <- as.factor(A22.interaction.transcripts.type$exp_type)
str(A22.interaction.transcripts.type)

# Ar
Ar.interaction.transcripts.type <- ddply(interaction.transcripts.TPM["Ar"], .(Transcript), RxNply)
Ar.interaction.transcripts.type$max.val <- as.numeric(Ar.interaction.transcripts.type$max.val)
Ar.interaction.transcripts.type$min.val <- as.numeric(Ar.interaction.transcripts.type$min.val)
Ar.interaction.transcripts.type$opt.exp <- as.numeric(Ar.interaction.transcripts.type$opt.exp)
Ar.interaction.transcripts.type$exp_type <- as.factor(Ar.interaction.transcripts.type$exp_type)
str(Ar.interaction.transcripts.type)

@@

```{r expression_exp_type_table, eval=TRUE, echo=FALSE, results='asis'}
# table type of response
A22.type.table <- table(responsive.transcripts.type[responsive.transcripts.type$colony == "A22", 'exp_type'])
Ar.type.table <- table(responsive.transcripts.type[responsive.transcripts.type$colony == "Ar", 'exp_type'])

exp_type.table <- rbind(A22.type.table, Ar.type.table)
rownames(exp_type.table) <- c("A22", "Ar")

pandoc.table(exp_type.table, style="rmarkdown", caption = "Number of transcripts with maximum expression at high, low, intermediate or both high and low (bimodal) temperatures.")
```

@@

```{r optimum_expression_comparison, cache=TRUE, eval=FALSE}
# list of transcripts that are 'high' expressed in A22
A22_high_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "A22" & responsive.transcripts.type$exp_type == "High"), "Transcript"]
# dataframe of transcripts from both colonies that are 'high' expressed in A22
A22_high_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% A22_high_transcripts), ]

@@

```{r Ar_low_wilcoxon}
# list of transcripts that are 'Low' expressed in Ar
Ar_low_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "Ar" & responsive.transcripts.type$exp_type == "Low"), "Transcript"]
# dataframe of transcripts from both colonies that are 'Low' expressed in Ar
Ar_low_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% Ar_low_transcripts), ]
dim(Ar_low_df)

@@

```{r intermediate_transcripts}
# list of transcripts that are 'Intermediate' expressed in A22
A22_int_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "A22" & responsive.transcripts.type$exp_type == "Intermediate"), "Transcript"]
A22_int_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% A22_int_transcripts), ]
A22_int_df$colony <- as.factor(A22_int_df$colony)

@@

# list of transcripts that are 'Intermediate' expressed in Ar
Ar_int_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "Ar" & responsive.transcripts.type$exp_type == "Intermediate"), "Transcript"]
Ar_int_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% Ar_int_transcripts), ]

@@

```{r calc_Intermediate_variance}
# extract 'Intermediate' expressed transcripts for A22 colony
setkey(TPM.dt.sub, Transcript)
A22trlist <- A22.interaction.transcripts.type[which(A22.interaction.transcripts.type$exp_type == "Intermediate"), "Transcript"]
A22.TPM.int.dt <- TPM.dt.sub[A22trlist]
setkey(A22.TPM.int.dt, colony)
A22.TPM.int.dt <- A22.TPM.int.dt["A22"]
str(A22.TPM.int.dt)

@@

# repeat for Ar
Artrlist <- Ar.interaction.transcripts.type[which(Ar.interaction.transcripts.type$exp_type == "Intermediate"), "Transcript"]
Ar.TPM.int.dt <- TPM.dt.sub[Artrlist]
setkey(Ar.TPM.int.dt, colony)
Ar.TPM.int.dt <- Ar.TPM.int.dt["Ar"]
str(Ar.TPM.int.dt)

@@

```{r calc_Bimodal_variance}
# extract 'Bimodal' expressed transcripts for A22 colony
A22trlist.bim <- A22.interaction.transcripts.type[which(A22.interaction.transcripts.type$exp_type == "Bimodal"), "Transcript"]
A22.TPM.bim.dt <- TPM.dt.sub[A22trlist.bim]
setkey(A22.TPM.bim.dt, colony)
A22.TPM.bim.dt <- A22.TPM.bim.dt["A22"]
str(A22.TPM.bim.dt)

@@

# repeat for Ar
Artrlist.bim <- Ar.interaction.transcripts.type[which(Ar.interaction.transcripts.type$exp_type == "Bimodal"), "Transcript"]
Ar.TPM.bim.dt <- TPM.dt.sub[Artrlist.bim]
setkey(Ar.TPM.bim.dt, colony)
Ar.TPM.bim.dt <- Ar.TPM.bim.dt["Ar"]
str(Ar.TPM.bim.dt)

@@

# faceted by type
png(paste(resultsdir, "CDF_expression_intermediate_interaction.png", sep=""))
g5 <- ggplot(interaction.transcripts.type, aes(x=max.val, group=colony)) + geom_density(alpha=0.2, position="identity")
g5 + facet_grid(. ~ exp_type) + scale_y_continuous(name="Density") +
  scale_x_continuous(name="Temperature of maximum expression")
dev.off()
```

@@

Use `selectTranscript` function to select transcripts based on 'exp_type'. As only significant transcripts have an 'exp_type' assigned, this is a small subset of the above.

```{r exp_type_function}
selectTranscript <- function(score) {
    return(score == 1)
}

# To select genes, add 'exp_type' to RxN df
RxNout.t <- merge(RxNout, Ap.exp_type, by="Transcript", all=TRUE)
length(which(!is.na(RxNout.t$exp_type)))
```

```{r bim.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.bim.geneList <- rep(0, length = nrow(RxNout.t))
Ap.bim.geneList[which(RxNout.t$exp_type=="Bimodal")] <- 1
names(Ap.bim.geneList) <- RxNout.t$Transcript
str(Ap.bim.geneList)
table(Ap.bim.geneList)

@@

```{r int.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.int.geneList <- rep(0, length = nrow(RxNout.t))
Ap.int.geneList[which(RxNout.t$exp_type=="Intermediate")] <- 1
names(Ap.int.geneList) <- RxNout.t$Transcript
str(Ap.int.geneList)
table(Ap.int.geneList)

@@

```{r hig.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.hig.geneList <- rep(0, length = nrow(RxNout.t))
Ap.hig.geneList[which(RxNout.t$exp_type=="High")] <- 1
names(Ap.hig.geneList) <- RxNout.t$Transcript
str(Ap.hig.geneList)
table(Ap.hig.geneList)

@@

```{r low.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.low.geneList <- rep(0, length = nrow(RxNout.t))
Ap.low.geneList[which(RxNout.t$exp_type=="Low")] <- 1
names(Ap.low.geneList) <- RxNout.t$Transcript
str(Ap.low.geneList)
table(Ap.low.geneList)

@@

# Same as p1, faceted by expression type
p3 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_line() +
  facet_grid(exp_type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p3

# Smooth plot, expression against temp, faceted by colony
p4 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_smooth() +
  facet_grid(exp_type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p4
```

@@

# Same as p1, faceted by expression type
p3 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_line() +
  facet_grid(exp_type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p3

# Smooth plot, expression against temp, faceted by colony
p4 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_smooth() +
  facet_grid(exp_type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p4
```

@@

# Same as p1, faceted by expression type
png(paste(resultsdir, "Ap_expression_by_colony_exp_line.png", sep=""))
  p3 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_line() +
    facet_grid(exp_type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p3
dev.off()

# Smooth plot, expression against temp, faceted by colony
png(paste(resultsdir, "Ap_expression_by_colony_exp_smooth.png", sep=""))
  p4 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_smooth() +
    facet_grid(exp_type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p4
dev.off()

@@

# Same as p1, faceted by expression type
png(paste(resultsdir, "Ap_expression_interaction_by_colony_exp_line.png", sep=""))
  p3 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_line() +
    facet_grid(exp_type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p3
dev.off()

# Smooth plot, expression against temp, faceted by colony
png(paste(resultsdir, "Ap_expression_interaction_by_colony_exp_smooth.png", sep=""))
  p4 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_smooth() +
    facet_grid(exp_type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p4
dev.off()
```

>>>>

```{r lmFunc}
# first, define function to use
lmFunc <- function(bar) {
  # fit lm
  lmout <- eval(parse(text = paste("lm(", model, ", data = bar)", sep = "")))  
  # stepAIC to drop non-significant terms
  f.lmout <- stepAIC(lmout)
  # return final model
  return(f.lmout) 
}

@@

response.type <- ldply(interaction.transcripts, .progress = "text", .inform = TRUE, RxNtype)

# plot
#qplot(val, pTPM, facets = .~colony, data = A22.pout, geom="smooth")

@@

# apply the 'RxNply' function to determine maximum and minimum temperatures of expression, as well as the expression level at the optimum temperature of 19.25C
temperature.transcripts.type <- ddply(temperature.transcripts.TPM, .(Transcript), RxNply)
temperature.transcripts.type$max.val <- as.numeric(temperature.transcripts.type$max.val)
temperature.transcripts.type$min.val <- as.numeric(temperature.transcripts.type$min.val)
temperature.transcripts.type$opt.exp <- as.numeric(temperature.transcripts.type$opt.exp)
temperature.transcripts.type$A22.exp.type <- as.factor(temperature.transcripts.type$A22.exp.type)

# repeat for transcripts that have an interaction with colongy
# A22
A22.interaction.transcripts.type <- ddply(interaction.transcripts.TPM["A22"], .(Transcript), RxNply)
A22.interaction.transcripts.type$max.val <- as.numeric(A22.interaction.transcripts.type$max.val)
A22.interaction.transcripts.type$min.val <- as.numeric(A22.interaction.transcripts.type$min.val)
A22.interaction.transcripts.type$opt.exp <- as.numeric(A22.interaction.transcripts.type$opt.exp)
A22.interaction.transcripts.type$A22.exp.type <- as.factor(A22.interaction.transcripts.type$A22.exp.type)
str(A22.interaction.transcripts.type)

# Ar
Ar.interaction.transcripts.type <- ddply(interaction.transcripts.TPM["Ar"], .(Transcript), RxNply)
Ar.interaction.transcripts.type$max.val <- as.numeric(Ar.interaction.transcripts.type$max.val)
Ar.interaction.transcripts.type$min.val <- as.numeric(Ar.interaction.transcripts.type$min.val)
Ar.interaction.transcripts.type$opt.exp <- as.numeric(Ar.interaction.transcripts.type$opt.exp)
Ar.interaction.transcripts.type$A22.exp.type <- as.factor(Ar.interaction.transcripts.type$A22.exp.type)
str(Ar.interaction.transcripts.type)

@@

```{r expression_A22.exp.type_table, eval=TRUE, echo=FALSE, results='asis'}
# table type of response
A22.type.table <- table(responsive.transcripts.type[responsive.transcripts.type$colony == "A22", 'A22.exp.type'])
Ar.type.table <- table(responsive.transcripts.type[responsive.transcripts.type$colony == "Ar", 'A22.exp.type'])

A22.exp.type.table <- rbind(A22.type.table, Ar.type.table)
rownames(A22.exp.type.table) <- c("A22", "Ar")

pandoc.table(A22.exp.type.table, style="rmarkdown", caption = "Number of transcripts with maximum expression at high, low, intermediate or both high and low (bimodal) temperatures.")
```

@@

```{r optimum_expression_comparison, cache=TRUE, eval=FALSE}
# list of transcripts that are 'high' expressed in A22
A22_high_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "A22" & responsive.transcripts.type$A22.exp.type == "High"), "Transcript"]
# dataframe of transcripts from both colonies that are 'high' expressed in A22
A22_high_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% A22_high_transcripts), ]

@@

```{r Ar_low_wilcoxon}
# list of transcripts that are 'Low' expressed in Ar
Ar_low_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "Ar" & responsive.transcripts.type$A22.exp.type == "Low"), "Transcript"]
# dataframe of transcripts from both colonies that are 'Low' expressed in Ar
Ar_low_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% Ar_low_transcripts), ]
dim(Ar_low_df)

@@

```{r intermediate_transcripts}
# list of transcripts that are 'Intermediate' expressed in A22
A22_int_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "A22" & responsive.transcripts.type$A22.exp.type == "Intermediate"), "Transcript"]
A22_int_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% A22_int_transcripts), ]
A22_int_df$colony <- as.factor(A22_int_df$colony)

@@

# list of transcripts that are 'Intermediate' expressed in Ar
Ar_int_transcripts <- responsive.transcripts.type[which(responsive.transcripts.type$colony == "Ar" & responsive.transcripts.type$A22.exp.type == "Intermediate"), "Transcript"]
Ar_int_df <- responsive.transcripts.type[which(responsive.transcripts.type$Transcript %in% Ar_int_transcripts), ]

@@

```{r calc_Intermediate_variance}
# extract 'Intermediate' expressed transcripts for A22 colony
setkey(TPM.dt.sub, Transcript)
A22trlist <- A22.interaction.transcripts.type[which(A22.interaction.transcripts.type$A22.exp.type == "Intermediate"), "Transcript"]
A22.TPM.int.dt <- TPM.dt.sub[A22trlist]
setkey(A22.TPM.int.dt, colony)
A22.TPM.int.dt <- A22.TPM.int.dt["A22"]
str(A22.TPM.int.dt)

@@

# repeat for Ar
Artrlist <- Ar.interaction.transcripts.type[which(Ar.interaction.transcripts.type$A22.exp.type == "Intermediate"), "Transcript"]
Ar.TPM.int.dt <- TPM.dt.sub[Artrlist]
setkey(Ar.TPM.int.dt, colony)
Ar.TPM.int.dt <- Ar.TPM.int.dt["Ar"]
str(Ar.TPM.int.dt)

@@

```{r calc_Bimodal_variance}
# extract 'Bimodal' expressed transcripts for A22 colony
A22trlist.bim <- A22.interaction.transcripts.type[which(A22.interaction.transcripts.type$A22.exp.type == "Bimodal"), "Transcript"]
A22.TPM.bim.dt <- TPM.dt.sub[A22trlist.bim]
setkey(A22.TPM.bim.dt, colony)
A22.TPM.bim.dt <- A22.TPM.bim.dt["A22"]
str(A22.TPM.bim.dt)

@@

# repeat for Ar
Artrlist.bim <- Ar.interaction.transcripts.type[which(Ar.interaction.transcripts.type$A22.exp.type == "Bimodal"), "Transcript"]
Ar.TPM.bim.dt <- TPM.dt.sub[Artrlist.bim]
setkey(Ar.TPM.bim.dt, colony)
Ar.TPM.bim.dt <- Ar.TPM.bim.dt["Ar"]
str(Ar.TPM.bim.dt)

@@

# faceted by type
png(paste(resultsdir, "CDF_expression_intermediate_interaction.png", sep=""))
g5 <- ggplot(interaction.transcripts.type, aes(x=max.val, group=colony)) + geom_density(alpha=0.2, position="identity")
g5 + facet_grid(. ~ A22.exp.type) + scale_y_continuous(name="Density") +
  scale_x_continuous(name="Temperature of maximum expression")
dev.off()
```

@@

Use `selectTranscript` function to select transcripts based on 'A22.exp.type'. As only significant transcripts have an 'A22.exp.type' assigned, this is a small subset of the above.

```{r A22.exp.type_function}
selectTranscript <- function(score) {
    return(score == 1)
}

# To select genes, add 'A22.exp.type' to RxN df
RxNout.t <- merge(RxNout, Ap.A22.exp.type, by="Transcript", all=TRUE)
length(which(!is.na(RxNout.t$A22.exp.type)))
```

```{r bim.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.bim.geneList <- rep(0, length = nrow(RxNout.t))
Ap.bim.geneList[which(RxNout.t$A22.exp.type=="Bimodal")] <- 1
names(Ap.bim.geneList) <- RxNout.t$Transcript
str(Ap.bim.geneList)
table(Ap.bim.geneList)

@@

```{r int.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.int.geneList <- rep(0, length = nrow(RxNout.t))
Ap.int.geneList[which(RxNout.t$A22.exp.type=="Intermediate")] <- 1
names(Ap.int.geneList) <- RxNout.t$Transcript
str(Ap.int.geneList)
table(Ap.int.geneList)

@@

```{r hig.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.hig.geneList <- rep(0, length = nrow(RxNout.t))
Ap.hig.geneList[which(RxNout.t$A22.exp.type=="High")] <- 1
names(Ap.hig.geneList) <- RxNout.t$Transcript
str(Ap.hig.geneList)
table(Ap.hig.geneList)

@@

```{r low.gsea, echo=TRUE, eval=TRUE}
# create geneList
Ap.low.geneList <- rep(0, length = nrow(RxNout.t))
Ap.low.geneList[which(RxNout.t$A22.exp.type=="Low")] <- 1
names(Ap.low.geneList) <- RxNout.t$Transcript
str(Ap.low.geneList)
table(Ap.low.geneList)

@@

# Same as p1, faceted by expression type
p3 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_line() +
  facet_grid(A22.exp.type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p3

# Smooth plot, expression against temp, faceted by colony
p4 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_smooth() +
  facet_grid(A22.exp.type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p4
```

@@

# Same as p1, faceted by expression type
p3 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_line() +
  facet_grid(A22.exp.type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p3

# Smooth plot, expression against temp, faceted by colony
p4 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
  geom_smooth() +
  facet_grid(A22.exp.type ~ colony) +
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
p4
```

@@

# Same as p1, faceted by expression type
png(paste(resultsdir, "Ap_expression_by_colony_exp_line.png", sep=""))
  p3 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_line() +
    facet_grid(A22.exp.type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p3
dev.off()

# Smooth plot, expression against temp, faceted by colony
png(paste(resultsdir, "Ap_expression_by_colony_exp_smooth.png", sep=""))
  p4 <- ggplot(temperature.transcripts.TPM, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_smooth() +
    facet_grid(A22.exp.type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p4
dev.off()

@@

# Same as p1, faceted by expression type
png(paste(resultsdir, "Ap_expression_interaction_by_colony_exp_line.png", sep=""))
  p3 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_line() +
    facet_grid(A22.exp.type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p3
dev.off()

# Smooth plot, expression against temp, faceted by colony
png(paste(resultsdir, "Ap_expression_interaction_by_colony_exp_smooth.png", sep=""))
  p4 <- ggplot(temperature.transcripts.TPM.interaction, aes(x=val, y=exp.scaled, group=Transcript)) +
    geom_smooth() +
    facet_grid(A22.exp.type ~ colony) +
    scale_y_continuous(name="Expression (scaled)") +
    scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
  p4
dev.off()
```
